Endogenous Politics and \\ the Design of Trade Institutions

### 2016-07-20 feedback.tex
add notes from 2014 spring Midwest mtgs

\subsection{From SITE 2016 presentation}
\begin{itemize}
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with contributions 'felonious'
	\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
	\item $\ga(e)$
		\begin{itemize}
			\item Giovanni: think of expost $\ga(e)$ as effort to elect/choose ex-post decision-maker
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Kyle (???): advertising paper (???)
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
		\end{itemize}
	\item Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies
		\begin{itemize}
			\item Maybe I should just get rid of tariff cap result altogether
		\end{itemize}
	\item David DeRemer: Safeguards have dropped off in use around the world
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Bob and Kyle: take my time, make it as good as possible. Better to have quality.
\end{itemize}

@@

\newpage
\section{Presentation Notes}
For SITE 2016
\begin{itemize}
	\item Ethier 2012 for protection decreasing function of $\tau$ [NEED TO REVISIT IN TEXT]. ``The Political-Support Approach to Protection,'' Global Journal of Economics
	\item $\ga(s)$ comes from MS 2011 QJE, ``The Role of Dispute Settlement Procedures in Trade Agreements''
	\item BS approach from 2002 book originates from 1999 AER ``An Economic Theory of GATT''
	\item Add title, axis to graph
	\item Review DSB literature (slide 13)
	\item Review my ex-ante results
\end{itemize}

>>>>

\subsection{From SITE 2016 presentation}
\begin{itemize}
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with contributions 'felonious'
	\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
		\begin{itemize}
			\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
			\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
		\end{itemize}
	\item $\ga(e)$
		\begin{itemize}
			\item Giovanni: think of expost $\ga(e)$ as effort to elect/choose ex-post decision-maker
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Kyle (???): advertising paper (???)
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
		\end{itemize}
	\item Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies
		\begin{itemize}
			\item Maybe I should just get rid of tariff cap result altogether
		\end{itemize}
	\item David DeRemer: Safeguards have dropped off in use around the world
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Bob and Kyle: take my time, make it as good as possible. Better to have quality.
\end{itemize}

@@

\newpage
\section{Feedback on 2014 draft}
\subsection{May 30, 2014, Spring Midwest meetings}
\begin{itemize}
	\item Rick Bond, Ian Wooton, James Lake, Mostafa, David Kuenzel at the talk
	\item James: need to be more precise about when $\ga$ is evaluated
\end{itemize}

\newpage
\section{Presentation Notes}
For SITE 2016
\begin{itemize}
	\item Ethier 2012 for protection decreasing function of $\tau$ [NEED TO REVISIT IN TEXT]. ``The Political-Support Approach to Protection,'' Global Journal of Economics
		\begin{itemize}
			\item Making $W$ quadratic in $\ga$ such as $\ga - \ga^2$ gives a nice interior max
		\end{itemize}
	\item $\ga(s)$ comes from MS 2011 QJE, ``The Role of Dispute Settlement Procedures in Trade Agreements''
	\item BS approach from 2002 book originates from 1999 AER ``An Economic Theory of GATT''
	\item Add title, axis to graph
	\item Review DSB literature (slide 13)
	\item Review my ex-ante results
\end{itemize}
